Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-20 papers/ms.tex
update ms

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar groups \citep[{\it
e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.  To date these
analyses have mostly clustered on stellar positions and 2-D
velocities.  One important result has been the discovery of
diffuse streams and tidal tails comparable in stellar mass to the
previously known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  Even
though these streams are spread over tens to hundreds of
parsecs, their velocity dispersions can remain coherent at the
$\sim$1\kms\ level.  Internal dynamics and projection effects can also
drive them to be much larger: in the Hyades,
stars in the tidal tails are expected to span up to $\pm 40\mkms$ in velocity
relative to the cluster center \citep{jerabkova_800_2021}.
The stars in such diffuse regions can be verified to be the same age
as the core cluster members through analyses of
color-absolute magnitude diagrams \citep{KounkelCovey2019}, stellar
rotation periods \citep{curtis_tess_2019,bouma_2021_ngc2516}, and
chemical abundances \citep{hawkins_2020}.  While there are 
implications for our understanding of star formation and cluster
evolution \citep{dinnbier_tidal_2020}, a separate consequence is that
we now know the ages of many more stars, including previously known
planet hosts.

The prime Kepler mission \citep{borucki_kepler_2010} found most of the
currently known transiting exoplanets, and it was conducted before
Gaia.  It is therefore sensible to revisit the Kepler field, given our
new knowlege of the stellar ages.

In this work, we expand on our earlier study of a $38^{+7}_{-6}$ Myr
old Neptune-sized planet in the Kepler field (Kepler-1627~Ab;
\citealt{bouma_kep1627_2022}).  This planet's age was derived
based on its host star's membership in the $\delta$\ Lyr\ cluster.
While our analysis of the cluster focused on the immediate vicinity of
Kepler-1627 in order to have a reasonable scope,  it became
clear that the $\delta$\ Lyr\ cluster seems to
also be part of a much larger group of similarly aged stars.  This
group, which is at a distance of $\sim$330\,pc from the Sun, 
spans Cepheus to Hercules (galactic longitudes, $l$, between
40$^\circ$ and 100$^\circ$), at galactic latitudes between
0$^\circ$ and 20$^\circ$.  We therefore refer to it as the Cep-Her
complex.  It exhibits significant sub-structure over its $\approx$250
parsec length, and a detailed analysis of its memberships, kinematics,
and possible origin is currently being prepared by R.~Kerr and
collaborators.

Here, our focus is on the intersection of the Cep-Her complex with the
Kepler field.  Cross-matching our Cep-Her members against known Kepler
Objects of Interest (KOIs; \citealt{thompson_planetary_2018}) yielded
four candidate cluster members: Kepler-1627, Kepler-1643, KOI-7368,
and KOI-7913.  Given our earlier analysis of Kepler-1627, we focus
here on the latter three objects.  After analyzing the relevant properties of
Cep-Her (Section~\ref{sec:cluster}), we derive the stellar properties
(Section~\ref{sec:stars}) and validate the planetary nature of each
system using a combination of the Kepler photometry and
high-resolution imaging (Section~\ref{sec:planets}).  We conclude with
a discussion of mini-Neptune size evolution, and point out possible
directions for future work (Section~\ref{sec:disc_conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points.  Kepler-1627 is in the outskirts of the $\delta$ Lyr
  cluster \citep{bouma_kep1627_2022}, which is centered at $\{ l, b\}
  \approx \{ 66^\circ, 12^\circ\}$.
  {\it Middle row}: Galactic positions.  The Sun is at $\{X, Y, Z\} =
  \{0, 0, 20.8\}$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  galactic longitudinal velocity versus galactic longitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 (magenta).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2'' (lime-green).
  The selection method for all of the stars displayed
  is described in Section~\ref{subsec:members}.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric, defined
such that the group member with the smallest core distance has a
weight of 1, the group member with the greatest core distance has a
weight of 0, and weights for the other group members are log-normally
distributed between these two extremes.  In Figure~\ref{fig:XYZvtang},
we show 12{,}436 objects with weight exceeding 0.02 as gray points,
and overplot 4{,}763 objects with weights exceeding 0.10 as black
points.\footnote{These counts only include objects with reliable
astrometry and photometry: $\varpi/\sigma_\varpi>5$;
$G/\sigma_{G}>50$; $G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm
BP}/\sigma_{G_{BP}}>20$.} The previously known $\delta$~Lyr\ cluster
is visible at $(l,b)=(68^\circ,15^\circ$) and $(v_{l'}, v_b)=(-4.5
,-4 )\mkms$.  RSG-5 is visible at $(l,b)=(83^\circ,6^\circ)$,
$(v_{l'}, v_b)=(5.5 ,-3.5 )\mkms$.  Most of the other
subclusters, including in Cep-Cyg ($l,b=90^\circ,7^\circ$) and
Cerberus ($l,b=48^\circ,18^\circ$) are too small or dispersed to have
previously been analyzed in great detail.

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
Our fourth and final step was to cross-match the candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members
with weights exceeding 0.02, this yielded
 yielded 11 were known false positives, 6 ``confirmed'' planets, and 8
 ``candidate'' planets.  
Inspection of the Kepler data validation summaries and Robovetter
classifications for these objects showed whether they were
potentially consistent with being {\it i)} planets, and {\it ii)}
$\lesssim 10^8$ years old, based on the presence of rotational
modulation at the expected period and amplitude \citep[{\it
e.g.},][Figure~9]{rebull_rotation_2020}.  Four objects remained after
this inspection: Kepler-1627, Kepler-1643, KOI-7368, and
KOI-7913.\footnote{These figures
yield an estimate of the size of Cep-Her: if our 4/14
possible matches represent the true positive rate, then
multiplying by the number of stars above our weight threshold
(12{,}436) yields $\approx$3{,}500 stars in the complex.}

@@

%
% Numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv
%
We define two sets of stars in the local vicinity of our objects of
interest.  For candidate RSG-5 members, we require:
\begin{align}
  X/{\rm pc} &\in [45, 75] \nonumber \\
  Y/{\rm pc} &\in [320, 350] \nonumber \\
  Z/{\rm pc} &\in [40, 70] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-4, -3] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [4, 6] \nonumber
\end{align}
For the diffuse stars near KOI-7368 and KOI-7913, we require
\begin{align}
  X/{\rm pc} &\in [20, 70] \nonumber \\
  Y/{\rm pc} &\in [230, 270] \nonumber \\
  Z/{\rm pc} &\in [75, 105] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-3.5, -1.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [2, 6] \nonumber
\end{align}
and we call this latter set of stars ``CH-2''.  These cuts yield 141
candidate RSG-5 members, and 37 candidate CH-2 members.
Tables of these stars are enumerated in Appendix~\ref{app:members}.
An important consideration, especially for CH-2, is the
contamination rate by field stars.  We assess this in the following
section.

@@

An independent way to assess the age of the candidate cluster members
is to measure their stellar rotation periods.  This approach can be
achieved using surveys such as TESS \citep{ricker_transiting_2015} and
the Zwicky Transient Facility (ZTF, \citealt{bellm_zwicky_2019});
it leverages a storied tradition of measuring rotation periods of stars in
benchmark open clusters \citep[see {\it
e.g.},][]{skumanich_time_1972,curtis_rup147_2020}.  The TESS data in
our case are especially useful, since they provide 3 to 5 lunar months
of photometry for all of our candidate CH-2 and RSG-5 members.

@@

The lower panels of Figure~\ref{fig:age} show the results.  In RSG-5,
36/42 stars have rotation periods faster than the Pleiades (86\%).
This numerator omits the two stars with periods $>$$12$\,days visible in
the lower-left panel of Figure~\ref{fig:age}.  The age interpretation
for these latter stars, particularly the $\approx$M2.5 dwarf, is not
obvious.  \citet{rebull_usco_2018} for instance have found numerous
M-dwarfs with 10-12 day rotation periods at ages of USco ($\sim$$8$\,Myr),
and some may still exist at ages of LCC ($\sim$$16$\,Myr;
L.~Rebull in preparation).  Regardless, given that nearly no field
star outliers seem to be present on the RSG-5 CAMD, the fact that we
do not detect rotation periods for $\approx$14\% of stars should
perhaps be taken as an indication for the fraction of stars for
which rotation periods might not be detectable, due to {\it e.g.}, pole-on
stars having lower amplitude starspot modulation.

@@

It is challenging to convert these stellar rotation periods to a
precise age estimate, since on the pre-main-sequence the stars are
spinning up due to thermal contraction rather than down due to
magnetized braking.  Regardless, the rotation period distributions of
both CH-2 and RSG-5 seem consistent with other 30\,Myr to 50\,Myr
clusters ({\it e.g.}, IC\,2602 and IC\,2391;
\citealt{douglas_stephanie_t_2021_5131306}).  They also seem
consistent with the false positive rates estimated from the
color-absolute magnitude diagrams.

@@

A few salient properties of the Kepler objects in Cep-Her can be
gleaned from Figure~\ref{fig:age}.  The stars span spectral types of
G8V (Kepler-1627) to K6V (KOI-7913 A).  The secondary in the KOI-7913
system has spectral type $\approx$K8V.  And given that a Solar-mass
star with solar metallicity arrives at the zero-age main sequence at
$t\approx40$ Myr \citep{choi_mesa_2016}, these stars are all in the
late stages of their pre-main-sequence contraction.  
% Their heliocentric distances are $\approx$260\,pc (KOI-7913 and
% KOI-7368, in CH-2) and $\approx$340\,pc (Kepler-1643, in RSG-5).

@@

\subsection{KOI-7368}
\paragraph{Spectra}
For KOI-7368, we acquired a spectrum on 2015 June 1 using the echelle
spectrograph (TRES; \citealt{furesz_tres_2008}) mounted at the
Tillinghast 1.5m at the Fred Lawrence Whipple Observatory.  The
stellar parameter classification pipeline for TRES has
been described by \citet{2021tsc2.confE.124B}.  It is based on the
synthetic template library constructed by
\citet{buchhave_hatp16b_class_2010}.  The resulting stellar parameters
($T_{\rm eff}, \log g, R_\star$) agreed with those from the
cluster-isochrone method within $1$-$\sigma$, though the effective
temperature was more precise by a factor of three.  Auxiliary
spectroscopic parameters included the metallicity $[{\rm Fe/H}]= -0.02
\pm 0.08$, the equatorial velocity $v\sin i = 20.21 \pm 0.50\,\mkms$,
and the systemic velocity ${\rm RV}_{\rm sys} = -10.9 \pm 0.2\,\mkms$.
The Li 6708\AA\ EW measurement procedure yielded ${\rm EW}_{\rm Li} =
236^{+16}_{-14}$\,m\AA.

@@

Systems such as K2-25, V1298~Tau, HIP-67522, TOI-837,
and TOI-1227 have sizes that are much larger than the picture we have
just described.  However, their large sizes can be accommodated
by existing models by invoking any of {\it i)} larger core masses,
{\it ii)} more volatile-rich compositions, {\it iii)}  larger initial
atmospheric mass fractions, or {\it iv)} longer thermal cooling times.
For instance, perhaps all five of the the aforementioned systems are
large simply because the planets are more massive than most
mini-Neptunes.  Secure mass measurements would help constrain this
parameter space, but the $\sim$1\,\kms\ spot-induced radial velocity
semi-amplitudes makes measuring the Doppler orbits incredibly
challenging.  \citep[][]{cale_diving_2021,zicher_one_2022,klein_one_2022}.
Regardless, the new Kepler-1643, KOI-7368, and KOI-7913 systems do
demonstrate that at least some planets at 40\,Myr have sizes that are
consistent with theoretical expectations for mini-Neptunes.  While
selection effects imposed by spot-induced photometric variability are
a likely explanation for why planets this small have not previously
been identified \citep[{\it e.g.},][]{zhou_2021_tois}, future work
should quantify this bias more carefully, in order to enable empirical
studies of how the planetary size distribution changes at early times.

@@

To quantify the density difference between CH-2 and RSG-5, we can compare the spatial and
velocity volumes searched for each group.
For RSG-5, we drew 141 candidate members from a $30\,{\rm
pc}\times30\,{\rm pc}\times30\,{\rm pc}$ spatial cube, given a $1 {\rm
\mkms} \times 2 {\rm \mkms }$ rectangle in apparent galactic velocity.
For CH-2, our 37 candidate members came from a rectangular prism of
dimension $50\,{\rm pc}\times40\,{\rm pc}\times30\,{\rm pc}$, and a
rectangular box of $2 {\rm \mkms} \times 4 {\rm \mkms}$.  If we define
the searched volume in units of ${\rm pc}^3\,{\rm km^2}\,{\rm s^{-2}}$, then
the volume ratio of CH-2 to RSG-5 is 9 to 1.  The number of candidate
members per unit searched volume in RSG-5 relative to CH-2 is
therefore 34 to 1.

Given its low density, in CH-2 really a star cluster?  For this
discussion, let us adopt the definition that a star cluster is a group
of at least 12 stars that was physically associated at its time of
formation.  The somewhat arbitrary ``12'' is set to distinguish star
clusters from high-order multiples \citep[see][]{krumholz_star_2019}.
Dissolved clusters and their tidal tails are therefore included in our
concept of clusters.  We do not require however that a particular number of stars per
unit spatial volume is required for a group to be a ``cluster''.
The latter point acknowledges that an important
factor in cluster identification is also the density in velocity
space.  Perhaps once stellar rotation periods and chemical abundances
reach the same level of ubiquity as stellar proper motions, they might
enable further refinement of our ability to discover stars that formed
together.

@@

\paragraph{Cep-Her}
Our analysis to date has focused only on portions of Cep-Her that were
observed by Kepler: RSG-5, CH-2, and the $\delta$~Lyr cluster.  The
membership and kinematics of the other subgroups shown in
Figure~\ref{fig:XYZvtang} deserve independent attention.  R.~Kerr and
collaborators have {\bf acquired N spectra} from which radial
velocities will be derived in their upcoming study, but if the
estimate that Cep-Her has $\approx$3{,}500 stars is correct then more
might be required to fully untangle the kinematics of the various
groups.  Wide-field spectroscopic surveys such as LAMOST
\citep{zhao_2012_LAMOST} or SDSS-V \citep{kollmeier_2017} could
provide sensitivity to the Li 6708\,\AA\ line, which would enable a
more detailed analysis of its abundance across the FGK members.  Gaia
DR3 may also provide RVS spectra for some of the brighter F and G
dwarfs, which would contain the calcium infrared triplet as another
age indicator.

A number of worthy photometric projects also seem possible given the
new understanding of the complex.  One is asteroseismology of the
$\delta$~Sct stars, using either TESS or Kepler data
\citep{bedding_very_2020}.  For cases in which the modes are resolved,
this might yield age estimates for subgroups independent from other
approaches.  Other projects could include searches of the Kepler light
curves for exocomets \citep{zieba_transiting_2019}, and for missed
planets around the most rapid rotators.

\paragraph{Exoplanet demographics at early times}
Our main motivation for finding new young planets is to help benchmark models
for planetary evolution.  However demographic analyses of the known planets
between $10^7$ and $10^9$ years have so far been somewhat limited.
Approximately 40 such planets are now known (Figure~\ref{fig:age}).  The
majority of published cases ($\approx$20) come from K2, though now $\approx$10
come from Kepler, and $\approx$10 from TESS.

>>>>

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar groups \citep[{e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.  To date these
analyses have mostly clustered on stellar positions and 2D
velocities.  One important result has been the discovery of
diffuse streams and tidal tails comparable in stellar mass to the
previously known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  Even
though these streams are spread over tens to hundreds of
parsecs, their velocity dispersions can remain coherent at the
$\sim$1\kms\ level.  Internal dynamics and projection effects can also
drive them to be much larger: in the Hyades,
stars in the tidal tails are expected to span up to $\pm 40\mkms$ in velocity
relative to the cluster center \citep{jerabkova_800_2021}.
The stars in such diffuse regions can be verified to be the same age
as the core cluster members through analyses of
color-absolute magnitude diagrams \citep{KounkelCovey2019}, stellar
rotation periods \citep{curtis_tess_2019,bouma_2021_ngc2516}, and
chemical abundances \citep{hawkins_2020}.  While there are 
implications for our understanding of star formation and cluster
evolution \citep{dinnbier_tidal_2020}, a separate consequence is that
we now know the ages of many more stars, including previously known
planet hosts.

The prime Kepler mission \citep{borucki_kepler_2010} found most of the
currently known transiting exoplanets, and it was conducted before
Gaia.  It is therefore sensible to revisit the Kepler field, given our
new knowledge of the stellar ages.

Here, we expand on our earlier study of a $38^{+7}_{-6}$ Myr
old Neptune-sized planet in the Kepler field (Kepler-1627~Ab;
\citealt{bouma_kep1627_2022}).  This planet's age was derived
based on its host star's membership in the $\delta$\ Lyr\ cluster.
While our analysis of the cluster focused on the immediate vicinity of
Kepler-1627 in order to have a reasonable scope,  it became
clear that the $\delta$\ Lyr\ cluster seems to
also be part of a much larger group of similarly aged stars.  This
group, which is at a distance of $\sim$330\,pc from the Sun, 
spans Cepheus to Hercules (galactic longitudes, $l$, between
40$^\circ$ and 100$^\circ$), at galactic latitudes between
0$^\circ$ and 20$^\circ$.  We therefore refer to it as the Cep-Her
complex.  It exhibits significant sub-structure over its $\approx$250
parsec length, and a detailed analysis of its memberships, kinematics,
and possible origin is currently being prepared by R.~Kerr and
collaborators.

Our focus is on the intersection of the Cep-Her complex with the
Kepler field.  Cross-matching our Cep-Her members against known Kepler
Objects of Interest (KOIs; \citealt{thompson_planetary_2018}) yielded
four candidate cluster members: Kepler-1627, Kepler-1643, KOI-7368,
and KOI-7913.  Given our earlier analysis of Kepler-1627, we focus
here on the latter three objects.  After analyzing the relevant properties of
Cep-Her (Section~\ref{sec:cluster}), we derive the stellar properties
(Section~\ref{sec:stars}) and validate the planetary nature of each
system using a combination of the Kepler photometry and
high-resolution imaging (Section~\ref{sec:planets}).  We conclude with
a discussion of mini-Neptune size evolution, and point out possible
directions for future work (Section~\ref{sec:disc_conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points.  Kepler-1627 is in the outskirts of the $\delta$ Lyr
  cluster \citep{bouma_kep1627_2022}, which is centered at $(l,b)
  \approx (66^\circ, 12^\circ)$.
  {\it Middle row}: Galactic positions.  The Sun is at $(X, Y, Z) =
  (0, 0, 20.8)$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  galactic longitudinal velocity versus galactic longitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 (magenta).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2'' (lime-green).
  The selection method for all of the stars displayed
  is described in Section~\ref{subsec:members}.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric, defined
such that the group member with the smallest core distance has a
weight of 1, the group member with the greatest core distance has a
weight of 0, and weights for the other group members are log-normally
distributed between these two extremes.  In Figure~\ref{fig:XYZvtang},
we show 12{,}436 objects with weight exceeding 0.02 as gray points,
and overplot 4{,}763 objects with weights exceeding 0.10 as black
points ({\bf @LGB: slightly more description of the ``weight'' parameter
is needed}).\footnote{These counts only include objects with reliable
astrometry and photometry: $\varpi/\sigma_\varpi>5$;
$G/\sigma_{G}>50$; $G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm
BP}/\sigma_{G_{BP}}>20$.} The previously known $\delta$~Lyr\ cluster
is visible at $(l,b)=(68^\circ,15^\circ$) and $(v_{l'}, v_b)=(-4.5
,-4 )\mkms$.  RSG-5 is visible at $(l,b)=(83^\circ,6^\circ)$,
$(v_{l'}, v_b)=(5.5 ,-3.5 )\mkms$.  Most of the other
subclusters, including in Cep-Cyg ($l,b=90^\circ,7^\circ$) and
Cerberus ($l,b=48^\circ,18^\circ$) are too small or dispersed to have
previously been analyzed in great detail.

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
Our fourth and final step was to cross-match the candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members
with weights exceeding 0.02, this yielded
 yielded 11 were known false positives, 6 ``confirmed'' planets, and 8
 ``candidate'' planets.  
Inspection of the Kepler data validation summaries and Robovetter
classifications for these objects showed whether they were
potentially consistent with being {\it i)} planets, and {\it ii)}
$\lesssim 10^8$ years old, based on the presence of rotational
modulation at the expected period and amplitude \citep[{e.g.},][Figure~9]{rebull_rotation_2020}.  Four objects remained after
this inspection: Kepler-1627, Kepler-1643, KOI-7368, and
KOI-7913.\footnote{These figures
yield an estimate of the size of Cep-Her: if our 4/14
matches represent the true positive rate, then
multiplying by the number of stars above our weight threshold
(12{,}436) yields $\approx$3{,}500 stars in the complex.  
This might however be an under-count,
since Kepler observed sparse 
regions of the complex, which are expected to have higher
contamination rates (Figure~\ref{fig:XYZvtang}, top panel).}

@@

%
% Numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv
%
We define two sets of stars in the local vicinity of our objects of
interest.  For candidate RSG-5 members, we require:
\begin{align}
  X/{\rm pc} &\in [45, 75] \nonumber \\
  Y/{\rm pc} &\in [320, 350] \nonumber \\
  Z/{\rm pc} &\in [40, 70] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-4, -3] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [4, 6] \nonumber
\end{align}
For the diffuse stars near KOI-7368 and KOI-7913, we require
\begin{align}
  X/{\rm pc} &\in [20, 70] \nonumber \\
  Y/{\rm pc} &\in [230, 270] \nonumber \\
  Z/{\rm pc} &\in [75, 105] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-3.5, -1.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [2, 6] \nonumber
\end{align}
and we call this latter set of stars ``CH-2''.  These cuts yield 141
candidate RSG-5 members, and 37 candidate CH-2 members.
These stars are listed in Appendix~\ref{app:members}, as are
the Cep-Her candidates that were observed by
Kepler.
An important consideration, especially for CH-2, is the
contamination rate by field stars.  We assess this in the following
section.

@@

An independent way to assess the age of the candidate cluster members
is to measure their stellar rotation periods.  This approach can be
achieved using surveys such as TESS \citep{ricker_transiting_2015} and
the Zwicky Transient Facility (ZTF, \citealt{bellm_zwicky_2019});
it leverages a storied tradition of measuring rotation periods of stars in
benchmark open clusters \citep[see {e.g.},][]{skumanich_time_1972,curtis_rup147_2020}.  The TESS data in
our case are especially useful, since they provide 3 to 5 lunar months
of photometry for all of our candidate CH-2 and RSG-5 members.

@@

The lower panels of Figure~\ref{fig:age} show the results.  In RSG-5,
36/42 stars have rotation periods faster than the Pleiades (86\%).
This numerator omits the two stars with periods $>$$12$\,days visible in
the lower-left panel of Figure~\ref{fig:age}.  The age interpretation
for these latter stars, particularly the $\approx$M2.5 dwarf, is not
obvious.  \citet{rebull_usco_2018} for instance have found numerous
M-dwarfs with 10-12 day rotation periods at ages of USco ($\sim$$8$\,Myr),
and some may still exist at ages of LCC ($\sim$$16$\,Myr;
L.~Rebull in preparation).  Regardless, given that nearly no field
star outliers seem to be present on the RSG-5 CAMD, the fact that we
do not detect rotation periods for $\approx$14\% of stars should
perhaps be taken as an indication for the fraction of stars for
which rotation periods might not be detectable, due to {e.g.}, pole-on
stars having lower amplitude starspot modulation.

@@

It is challenging to convert these stellar rotation periods to a
precise age estimate, since on the pre-main-sequence the stars are
spinning up due to thermal contraction rather than down due to
magnetized braking.  Regardless, the rotation period distributions of
both CH-2 and RSG-5 seem consistent with other 30\,Myr to 50\,Myr
clusters ({e.g.}, IC\,2602 and IC\,2391;
\citealt{douglas_stephanie_t_2021_5131306}).  They also seem
consistent with the false positive rates estimated from the
color-absolute magnitude diagrams.

@@

A few salient properties of the Kepler objects in Cep-Her can be
gleaned from Figure~\ref{fig:age}.  The stars span spectral types of
G8V (Kepler-1627) to K6V (KOI-7913 A).  The secondary in the KOI-7913
system has spectral type $\approx$K8V.  And given that a star with Solar mass
and metallicity arrives at the zero-age main sequence at
$t\approx40$ Myr \citep{choi_mesa_2016}, these stars are all in the
late stages of their pre-main-sequence contraction.  
% Their heliocentric distances are $\approx$260\,pc (KOI-7913 and
% KOI-7368, in CH-2) and $\approx$340\,pc (Kepler-1643, in RSG-5).

@@

\subsection{KOI-7368}
\paragraph{Spectra}
For KOI-7368, we acquired a spectrum on 2015 June 1 using the echelle
spectrograph (TRES; \citealt{furesz_tres_2008}) mounted at the
Tillinghast 1.5m at the Fred Lawrence Whipple Observatory.  The
Stellar Parameter Classification pipeline for TRES has
been described by \citet{2021tsc2.confE.124B}.  It is based on the
synthetic template library constructed by
\citet{Buchhave2012}.  The resulting stellar parameters
($T_{\rm eff}, \log g, R_\star$) agreed with those from the
cluster-isochrone method within $1$-$\sigma$, though the effective
temperature was more precise by a factor of three.  Auxiliary
spectroscopic parameters included the metallicity $[{\rm Fe/H}]= -0.02
\pm 0.08$, the equatorial velocity $v\sin i = 20.21 \pm 0.50\,\mkms$,
and the systemic velocity ${\rm RV}_{\rm sys} = -10.9 \pm 0.2\,\mkms$.
The Li 6708\AA\ EW measurement procedure yielded ${\rm EW}_{\rm Li} =
236^{+16}_{-14}$\,m\AA.

@@

Systems such as K2-25, V1298~Tau, HIP-67522, TOI-837,
and TOI-1227 have sizes that are much larger than the picture we have
just described.  However, their large sizes can be accommodated
by existing models by invoking any of {\it i)} larger core masses,
{\it ii)} more volatile-rich compositions, {\it iii)}  larger initial
atmospheric mass fractions, or {\it iv)} longer thermal cooling times.
For instance, perhaps all five of the the aforementioned systems are
large simply because the planets are more massive than most
mini-Neptunes.  Secure mass measurements would help constrain this
parameter space, but the $\sim$1\,\kms\ spot-induced radial velocity
semi-amplitudes makes measuring the Doppler orbits incredibly
challenging.  \citep[][]{cale_diving_2021,zicher_one_2022,klein_one_2022}.
Regardless, the new Kepler-1643, KOI-7368, and KOI-7913 systems do
demonstrate that at least some planets at 40\,Myr have sizes that are
consistent with theoretical expectations for mini-Neptunes.  While
selection effects imposed by spot-induced photometric variability are
a likely explanation for why planets this small have not previously
been identified \citep[{e.g.},][]{zhou_2021_tois}, future work
should quantify this bias more carefully, in order to enable empirical
studies of how the planetary size distribution changes at early times.

@@

To quantify the density difference between CH-2 and RSG-5, we can compare the spatial and
velocity volumes searched for each group.
For RSG-5, we drew 141 candidate members from a $30\,{\rm
pc}\times30\,{\rm pc}\times30\,{\rm pc}$ spatial cube, given a $1 {\rm
\mkms} \times 2 {\rm \mkms }$ rectangle in apparent galactic velocity.
For CH-2, our 37 candidate members came from a rectangular prism of
dimension $50\,{\rm pc}\times40\,{\rm pc}\times30\,{\rm pc}$, and a
rectangular box of $2 {\rm \mkms} \times 4 {\rm \mkms}$.  If we define
the searched volume in units of ${\rm pc}^3\,{\rm km^2}\,{\rm s^{-2}}$, then
the volume ratio of CH-2 to RSG-5 is 9 to 1.  The ratio of number
densities (candidate members per unit searched volume) in RSG-5
relative to CH-2 is 34 to 1.

Given its low density, in CH-2 really a star cluster?  For this
discussion, we adopt the definition that a star cluster is a group
of at least 12 stars that was physically associated at its time of
formation.  The somewhat arbitrary ``12'' is set to distinguish star
clusters from high-order multiples \citep[see][]{krumholz_star_2019}.
Dissolved clusters and their tidal tails are therefore included in our
concept of clusters.  We do not require however that a particular number of stars per
unit spatial volume is required for a group to be a ``cluster''.
The latter point acknowledges that an important
factor in cluster identification is also the density in velocity
space.  Perhaps once stellar rotation periods and chemical abundances
reach the same level of ubiquity as stellar proper motions, they might
enable further refinement of our ability to discover stars that formed
together.

@@

\paragraph{Cep-Her}
Our analysis to date has focused only on portions of Cep-Her that were
observed by Kepler: RSG-5, CH-2, and the $\delta$~Lyr cluster.  The
membership and kinematics of the other subgroups shown in
Figure~\ref{fig:XYZvtang} deserve independent attention.  R.~Kerr and
collaborators have {\bf acquired N spectra} from which radial
velocities will be derived in their upcoming study.
One important aspect of these analyses will be to assess whether the 
traceback approach could be applicable.
However if the
estimate that Cep-Her has $\gtrsim$3{,}500 stars is correct then more
data might be required to fully untangle the kinematics of the various
groups.  Wide-field spectroscopic surveys such as LAMOST
\citep{zhao_2012_LAMOST} or SDSS-V \citep{kollmeier_2017} could
enable such analyses, while also
providing sensitivity to the Li 6708\,\AA\ line.  Gaia
DR3 may also provide RVS spectra for some of the brighter F and G
dwarfs, which would contain the calcium infrared triplet as another
age indicator.

A number of worthy photometric projects also seem possible given the
new understanding of the complex.  One is asteroseismology of the
$\delta$~Sct stars, using either TESS or Kepler data
\citep{bedding_very_2020}.  For cases in which the modes are resolved,
this might yield age estimates for the subgroups independent of other
approaches.  Other projects could include searches of the Kepler light
curves for exocomets \citep{zieba_transiting_2019}, and for missed
planets around the most rapid rotators.

\paragraph{Exoplanet demographics at early times}
Our main motivation for finding new young planets is to help benchmark models
for planetary evolution.  However demographic analyses of the known planets
between $10^7$ and $10^9$ years have so far been somewhat limited.
Approximately 40 such planets are now known (Figure~\ref{fig:age}).
About half come from K2, a quarter from TESS, and now a quarter from
Kepler.

Given the current state of the field, a few reflections regarding experimental
design of a demographic survey focused on planetary evolution during
the first gigayear might be useful.  The first is that such a project
requires a set of
target stars with known ages.  The best way to
compile relevant stars right now is likely by combining automated
spatio-kinematic clustering from Gaia with rotation periods measured using TESS
\citep[see the appendices of][]{bouma_kep1627_2022}.  The second consideration
is that the known young planets smaller than $3$\,$R_\oplus$ all come from either
K2 or Kepler.  Demographic inferences based on TESS are therefore limited to
planetary sizes $\gtrsim4$\,$R_\oplus$, for planets close-in to their host stars.  It
seems worthwhile to compare the absolute occurrence rate of such planets to
those observed by Kepler.  One specific question that seems within reach would
be to clarify whether enough young stars have been searched for the dearth of
young hot Jupiters to be significant.  Since the
hot Jupiter occurrence rate is strongly dependent on stellar mass and
metallicity \citep{petigura_metallicity_2018,petigura_cksX_2022}, particular
care would be needed to select a sample of well-studied FGK dwarfs for the
measurement, likely using stars in Sco OB2, Cep-Her, and Orion.  For
demographic studies focused on how mini-Neptune sizes evolve, the combined K2
and Kepler dataset might be the better primary source.
